---
title: "Schedule Scrapping"
output:
  pdf_document: default
  html_notebook: default
name: Makena Haroldson
---
### Introduction

Csu Chico's Spring 2019 and 2020 Math and Csci courses

```{r}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}
suppressMessages(include("rvest"))
suppressMessages(include("tidyr"))
suppressMessages(include("dplyr"))
suppressMessages(include("stringr"))
```

### Class Schedule Function

This is a function that we will be using to transfer information from websites. Note that one the website they had two types of classes: a regular classes(ex. lecture) and alternative class(ex. labs and activity). However, the website did not maintain a consistent order and so we will import class composition so we can keep track of each type.
```{r}
read_class_schedule <- function(url){
  url_html <- read_html(url)

#obtain semester and year of courses
Semester <-url_html %>% 
              html_nodes(".subjpagessubjheader") %>% 
              html_text()

str_semester <- str_extract(Semester,"[a-z,A-z]+ [0-9]+")

#obtain regular classes information
classes <- url_html %>% html_nodes(".classrow")

subj <- classes %>% 
              html_nodes("td.subj") %>% 
              html_text()
course_num <- classes %>% 
              html_nodes("td.cat_num") %>% 
              html_text() 
course_sect <- classes %>% 
              html_nodes("td.sect") %>% 
              html_text() %>% 
              as.integer()
course_comp <- classes %>% 
              html_nodes("td.comp") %>% 
              html_text() 
title <- classes %>% 
              html_nodes("td.title") %>% 
              html_text()
instructor <- classes %>% 
              html_nodes("td.Instructor") %>% 
              html_text()
total_enroll <- classes %>% 
          html_nodes("td.enrtot") %>% 
          html_text() %>% 
          as.integer()

#obtain regular classes information
classes_alt <- url_html %>% html_nodes(".classrowalt")

subj_a <- classes_alt %>% 
              html_nodes("td.subj") %>% 
              html_text()
course_num_a <- classes_alt %>% 
              html_nodes("td.cat_num") %>% 
              html_text()
course_sect_a <- classes_alt %>% 
              html_nodes("td.sect") %>% 
              html_text() %>% 
              as.integer()
course_comp_a <- classes_alt %>% 
              html_nodes("td.comp") %>% 
              html_text() 
title_a <- classes_alt %>% 
              html_nodes("td.title") %>% 
              html_text()
instructor_a <- classes_alt %>% 
              html_nodes("td.Instructor") %>% 
              html_text()
total_enroll_a <- classes_alt %>% 
          html_nodes("td.enrtot") %>% 
          html_text() %>% 
          as.integer()

#create tables of regular classes
class_table <- tibble(semester=str_semester, subj=subj, course_num=course_num, sect=course_sect, comp=course_comp, title=title, instructor=instructor,  total_enroll=total_enroll)

#create tables of alterbative classes
alt_class_tables <- tibble(semester=str_semester, subj=subj_a, course_num=course_num_a, sect=course_sect_a, comp=course_comp_a, title=title_a, instructor=instructor_a, total_enroll=total_enroll_a)

#merge the two tables together
course_table <- bind_rows(class_table,alt_class_tables)

#separate the semester and year into individual columns
course_table <- separate(course_table, semester, into= c("semester","year"), sep= " ")

#merge a course subject and number columns together
course_table$course <- paste(course_table$subj, course_table$course_num)

#delete the unused columns
course_table <- subset(course_table, select = -c(subj,course_num))

#reorder columns
course_table <- course_table[,c(1,2,8,3,4,5,6,7)]

return(course_table)
}
```

### Importation and Merging

Here we are importing the website's urls.
```{r}
CS19S_url <- "http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml"

CS20S_url <- "http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml"

Mh19S_url <- "http://ems.csuchico.edu/APSS/schedule/spr2019/MATH.shtml"

Mh20S_url <- "http://ems.csuchico.edu/APSS/schedule/spr2020/MATH.shtml"
```

Now we call the function from above and send in each url. After we have all our tables, we will then merge all 4 into 1 table.
```{r}
Csci19_table <- read_class_schedule(url = CS19S_url)
View(Csci19_table)

Csci20_table <-  read_class_schedule(url = CS20S_url)
View(Csci20_table)

Math19_table <-  read_class_schedule(url = Mh19S_url)
View(Math19_table)

Math20_table <-  read_class_schedule(url = Mh20S_url)
View(Math20_table)

#merge the 4 tables together
Courses_table <- bind_rows(Csci19_table,Csci20_table)
Courses_table <- bind_rows(Courses_table,Math19_table)
Courses_table <- bind_rows(Courses_table,Math20_table)
View(Courses_table)
```







